---
title: "SQL RMarkdown"
author: "Zoë Turner"
date: "28/01/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}

library(odbc) # necessary for connecting to SQL server

```

# Setting up multiple server connections

The code chunk is R and uses the {odbc} drivers. The default connection as "con" is set
along with the global chunk settings (in this case evaluation is off as there is no SQL connection).

```{r database-connections}
con <- dbConnect(odbc(),
                 Driver = "SQL Server",
                 Server = "<ServerName>",
                 Database = "<DatabaseName>",
                 Trusted_Connection = "True") # uses windows authentication so password not required

con_server2 <- dbConnect(odbc(),
                 Driver = "SQL Server",
                 Server = "<ServerName>",
                 Database = "<DatabaseName>",
                 Trusted_Connection = "True")

con_server3 <- dbConnect(odbc(),
                 Driver = "SQL Server",
                 Server = "<ServerName>",
                 Database = "<DatabaseName>",
                 Trusted_Connection = "True")

# This sets the default connection to "con"
knitr::opts_chunk$set(connection = "con",
                      eval = FALSE,
                      echo = TRUE)
```

## Naming tables

Tables as they are brought into R are named in the chunk `output.var=""`

## con_server2

```{sql connection="con_server2", output.var="server2_dates"}

SELECT Top 100 *
FROM DIM.Date

```

## con_server3

```{sql connection="con_server3", output.var="server3_dates"}

SELECT Top 100 *
FROM DIM.Date

```


## Default connection

No connection is needed as this is detailed in the setup chunk
     
```{sql, output.var="default_dates" }

SELECT Top 100 *
FROM DIM.Date

```

Would be the same as 

```{sql connection="con", output.var="default_dates" }

SELECT Top 100 *
FROM DIM.Date

```
